The investment strategy based on behavior of artificial earthworm for use in algotrading

### 2014-04-15 Article/Article20140406Granada/LatexArt/article_main.tex
which shows the individual steps

\begin{itemize}
\item To determine the current quality of the strategy and risk management summation of current gains/losses (the accumulation) is performed
\begin{equation}
Zci = sum ( Zi ) \text{ from } i = 1 \text{ to the current i value;}
\end{equation}
\item There is a possible local subsidence Zci capital by introducing two additional parameters to manage the risk.\\
p3 --- the number of steps back on the curve of the cumulative profit for the determination of Zci --- p3 for comparison with the present value of Zci;
p4 --- maximum size of the capital subsidence (eg for the currency pair EURUSD measured in pips), which if exceeded will trigger the closure position:\\
\begin{equation}
\text{If } ( Zci - p3 - Zi ) <- p4 \text{ and } PositionState \neq 0 \text{ then } PositionState = 0
\end{equation} 
where PositionState --- is the type of open position (long or short) and PositionStates equal 0 means resignations from the opening position to the beginning of the next candle.
\end{itemize}
So, the above-described algorithm uses 5 parameters, as many as 3 of which are devoted to risk management strategy.\\
%%PBStart
The complexity of the algorithm is illustrated in Figure \ref{fig:fig7}, which in the form of a decision tree shows the individual steps and decisions made in the iteration on a single candle. This iteration was carried out both in the search for optimal parameters p1, ..., p5 and in the process they use in the testing phase for data not used in learning.\\

>>>>

\begin{itemize}
\item To determine the current quality of the strategy and risk management summation of current gains/losses (the accumulation) is performed
\begin{equation}
Zci = sum ( Zi ) \text{ from } i = 1 \text{ to the current i value;}
\end{equation}
\item There is a possible local subsidence Zci capital by introducing two additional parameters to manage the risk.\\
p3 --- the number of steps back on the curve of the cumulative profit for the determination of Zci --- p3 for comparison with the present value of Zci;
p4 --- maximum size of the capital subsidence (eg for the currency pair EURUSD measured in pips), which if exceeded will trigger the closure position:\\
\begin{equation}
\text{If } ( Zci - p3 - Zi ) <- p4 \text{ and } PositionState \neq 0 \text{ then } PositionState = 0
\end{equation} 
where PositionState --- is the type of open position (long or short) and PositionStates equal 0 means resignations from the opening position to the beginning of the next candle.
\end{itemize}
So, the above-described algorithm uses 5 parameters, as many as 3 of which are devoted to risk management strategy.\\
%%PBStart
The complexity of the algorithm is illustrated in Figure \ref{fig:fig7}, which shows the individual steps and decisions made in the iteration on a single candle in the form of a decision tree. This iteration was carried out both in the search for optimal parameters p1, ..., p5 and in the process they use in the testing phase for data not used in learning.\\
